---
title: "Appifyr Input Types"
output: 
  html_document: 
    toc: yes
    toc_float: true
---

Appifyr offers three types of inputs: dropdown, text and number. All input types share the arguments `label` and `width`. The label will be displayed next to the input on the form. The width argument accepts values between 1 and 12 (it's using the bootstrap grid system). A value of 12 will make the input take an entire row. The default width is 4.

```{r, echo=FALSE}
library(appifyr)
library(stringr)
```


# Text 

The text input `inp_text` is the most basic type of input.

```{r}
appify("text_to_title", inps = list(plot_title = inp_text(width = 12)))
```

# Number

You can use the number input `inp_number` type to restrict values to numbers.

```{r}
appify("number_to_sample", inps = list(n = inp_number(from = 0, to = 10e9)))
```

# Dropdown

## Atomic Argument

```{r}
appify("dropdown_to_filter", 
       inps = list(flower = inp_dropdown(unique(iris$Species))))
```

## List Argument

```{r}
flowers <- list(
  Setosa = "setosa",
  Versicolor = "versicolor",
  Virginica = "virginica"
)
appify("dropdown_to_filter", inps = list(flower = inp_dropdown(flowers)))
```

## Data Frame Argument

```{r, warning=FALSE}
flowers <- data.frame(value = unique(iris$Species)) %>% 
  mutate(key = str_to_title(value))
appify("dropdown_to_filter", inps = list(flower = inp_dropdown(flowers)))
```

