---
title: "Appifyr Input Types"
output: 
  html_document: 
    toc: yes
    toc_float: true
---

Appifyr offers three types of inputs: dropdown, text and number. 

All input types share the arguments `label` and `width`. The label will be displayed next to the input on the form. The width argument accepts integer values between 1 and 12 (it's using the bootstrap grid system). A value of 12 will make the input take an entire row. The default width is 4.

The `inps` argument takes a list where every element is named corresponding to one of the arguments to your function. So, for a function `my_function(x, y)` you must specify both `x` and `y` in the list, e.g. `list(x = inp_text(), y = inp_text())`. The names must match exactly. Note that it is possible to pass anything to `...`.  

```{r, echo=FALSE}
library(appifyr)
library(stringr)
```


# Text 

The text input `inp_text` is the most basic type of input.

```{r}
appify("text_to_title", inps = list(plot_title = inp_text(width = 12)))
```

# Number

You can use the number input `inp_number` type to restrict values to numbers.

```{r}
appify("number_to_sample", inps = list(n = inp_number(from = 0, to = 10e9)))
```

# Dropdown

Appifyr's function `inp_dropdown` accepts atomics, lists and datafarmes as arguments. Intrnally, appifyr always converts to a dataframe.

## Atomic Argument

When given a vector as the first argument the keys will be equal to the values passed to the function.

```{r}
appify("dropdown_to_filter", 
       inps = list(flower = inp_dropdown(unique(iris$Species))))
```

## List Argument

A list should be used when one deals with a fairly small number of levels and needs specific names for those. The format is intuitive: `list(key1 = "value1", key2 = "value2")`.

```{r}
flowers <- list(
  Setosa = "setosa",
  Versicolor = "versicolor",
  Virginica = "virginica"
)
appify("dropdown_to_filter", inps = list(flower = inp_dropdown(flowers)))
```

## Data Frame Argument

The dataframe argument needs a specific format. There must be exactly two columns `key` and `value`. This type of passing the levels is most useful when one wants to create a large number of levels.

```{r, warning=FALSE}
flowers <- data.frame(value = unique(iris$Species)) %>% 
  mutate(key = str_to_title(value))
appify("dropdown_to_filter", inps = list(flower = inp_dropdown(flowers)))
```

